```{r opts, echo=FALSE, message=FALSE}
opts_knit$set(base.dir=outdir, toc='true')
```
```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```

# Rqc `r packageVersion("Rqc")` - Quality Control Report

## Average Quality
This plot describes the average quality pattern by showing on the
X-axis quality thresholds and on the Y-axis the percentage of reads
that exceed that quality level.
```{r average-quality-plot, fig.width=10}
rqcReadQualityPlot(rqcResultSet)
```

## Cycle-specific Average Quality
This describes the average quality scores for each cycle of sequencing.
```{r cycle-average-quality-plot, fig.width=10}
rqcCycleAverageQualityPlot(rqcResultSet)
```

## Read Length Distribution
Barplot that presents the distribuition of the lengths of the reads available in the FASTQ file.
```{r read-width-plot, fig.width=10}
rqcReadWidthPlot(rqcResultSet)
```

## Cycle-specific GC Content
Line plot showing the average GC content for every cycle of sequencing.
```{r cycle-gc-plot, fig.width=10}
rqcCycleGCPlot(rqcResultSet)
```

## Cycle-specific Quality Distribution
Bar plot showing the proportion of quality calls per cycle. Colors are
presented in a gradient Red-Blue, where red identifies calls of lower
quality. This visualization is preferred as it is cleaner than the
boxplots described below.
```{r cycle-quality-plots, fig.width=10}
rqcCycleQualityPlot(rqcResultSet)
```

## Cycle-specific Quality Distribution - Boxplot
Boxplots describing empirical patterns of quality distribution on each cycle of sequencing.
```{r cycle-quality-boxplots, fig.width=10}
rqcCycleQualityBoxPlot(rqcResultSet)
```

## Cycle-specific Base Call Proportion
This bar plot describes the proportion of each nucleotide called for every cycle of sequencing.
```{r cycle-basecall-plots, fig.width=10}
rqcCycleBaseCallsPlot(rqcResultSet)
```
